Gaussian Processes Autoregressive Models for Forecasting the Disturbance Storm Time Index

### 2016-11-10 Response-Referees.tex

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Model_RMSE_validationStorms}
      \caption{Averaged RMSE performance of \emph{GP-ARX} models for different values of auto-regressive order $p$}
         \label{fig:prmse}
 \end{figure}

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Model_corr_validationStorms}
      \caption{Averaged Correlation Coefficient of \emph{GP-ARX} models for different values of auto-regressive order $p$}
         \label{fig:pcorr}
 \end{figure}

\item \emph{The time lag parameters 'p' for the two models were selected by comparing the model to the 63 storm events. Shouldn't the parameter have been selected using an independent set of storms instead in order not to favor these new models against the other models?}

Additions were made in lines $246-253$ in section 4. \blockquote{The time lags chosen for \emph{GP-AR} are $p = 6$ while for \emph{GP-ARX} they are $p=6$, $p_{ex} = 1$. These values are arrived at by building \emph{GP-AR} and \emph{GP-ARX} models for different values of $p$ and choosing the model yielding the best performance on a set of storm events during the periods $1995-1997$ and $2011-2014$.

Box plots \ref{fig:prmse} and \ref{fig:pcorr} show the performance of \emph{GP-ARX} models having values of $p={3,4,5,6,7}$. We observe that the median \emph{RMSE} and \emph{CC} degrade slightly from $p = 3$ to $p = 7$ and models with $p = 6$ have a much smaller variance in performance making them more robust to outliers. The choice of $p = 6$ thus gives a good trade off between model robustness and complexity.

### 2016-11-10 swsc.tex
Updates from ShareLaTeX

The time lags chosen for \emph{GP-AR} are $p = 6$ while for \emph{GP-ARX} $p=6$, $p_{ex} = 1$ are arrived by experimenting with values starting from one and choosing the value of $p$ yielding best performance on a separate set of storm events during the periods $1995-1997$ and $2011-2014$. Figures \ref{fig:prmse} and \ref{fig:pcorr} show the performance of \emph{GP-ARX} models having values of $p={3,4,5,6,7}$. We observe that the median \emph{RMSE} and \emph{CC} degrade slightly from $p = 3$ to $p = 7$ and models with $p = 6$ have a much smaller variance in performance making them more robust to outliers. The choice of $p = 6$ thus gives a good trade off between model robustness and complexity.

>>>>

The time lags chosen for \emph{GP-AR} are $p = 6$ while for \emph{GP-ARX} they are $p=6$, $p_{ex} = 1$. These values are arrived at by building \emph{GP-AR} and \emph{GP-ARX} models for different values of $p$ and choosing the model yielding the best performance on a set of storm events during the periods $1995-1997$ and $2011-2014$.

Box plots \ref{fig:prmse} and \ref{fig:pcorr} show the performance of \emph{GP-ARX} models having values of $p={3,4,5,6,7}$. We observe that the median \emph{RMSE} and \emph{CC} degrade slightly from $p = 3$ to $p = 7$ and models with $p = 6$ have a much smaller variance in performance making them more robust to outliers. The choice of $p = 6$ thus gives a good trade off between model robustness and complexity.
